---
title: "BUA_455_Week_12"
author: "Penelope Pooler Eisenbies"
date: "2022-11-15"
output: 
  html_document: 
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=TRUE}

# this line specifies options for default options for all R Chunks
knitr::opts_chunk$set(echo=T, 
                      highlight=T)

# suppress scientific notation
options(scipen=100,
        getSymbols.warning4.0 = FALSE)

# install helper package (pacman), if needed
if (!require("pacman")) install.packages("pacman", repos = "http://lib.stat.cmu.edu/R/CRAN/")

# install and load required packages
# pacman should be first package in parentheses and then list others
pacman::p_load(pacman,tidyverse, ggthemes, magrittr, knitr, lubridate, gridExtra, RColorBrewer, 
               flexdashboard, maps, usdata, countrycode, mapproj, shadowtext, plotly, grid)

# verify packages (comment out in finished documents)
p_loaded()

```

---

### Updates

- HW 2 - Part 5 is due Friday, 11/18.  

  - For Question 9, you should document steps to update Panel 6.
  
  - Data for this panel were updated this week:
  
    - [Netflix Quarterly Revenue (requires SU login)](https://www-statista-com.libezproxy2.syr.edu/statistics/273883/netflixs-quarterly-revenue/)
    - [Netflix Quarterly Net Income (requires SU login)](https://www-statista-com.libezproxy2.syr.edu/statistics/273884/netflixs-quarterly-net-income/)

  - There is a grace period (over break), but you should be able to finish it before then.
  
---

### More Updates

- Quiz 2 grading is progressing

- Proposal Feedback will be posted this week.

  - Note: One group has asked to ammend their proposal and I agreed.  If your group is considering a switch, this would be the last week that it would be feasible.
  
- If you have data management questions, get in touch with me or a TA ASAP
  
  - Plan out tasks and how to accomplish them.  
  
  - We are here to help with tasks where you might be stymied, but don't wait until the last day.
  
- Presentations will be on 12/6 and 12/8.  

  - All students are required to attend and provide feedback.

---

### Plan for this Week

- More examples and skills to manage and curate geographic data

  - Today - World Data
  
  - Thursday - State data, Filtering to a Region, Publisng work

- More tips for good project management

- Posting HTML files for free using **[Rpubs](https://rpubs.com/)** 

  - Useful for presenting dashboard
  
---

### Importing and Joining World Datasets

#### World Data 

```{r world data prep}

world <- map_data("world") |> select(!subregion)                              # world geo info
intbxo <- read_csv("intl_bxo.csv", show_col_types = F, skip=6) |>             # import/tidy bxo
  select(1,6) |>
  rename("region" = "Area", "wknd_gross" = "Weekend Gross") |>
  filter(!is.na(wknd_gross)) |>
  mutate(wknd_gross = gsub("$", "", wknd_gross, fixed = T),
         wknd_gross = gsub(",", "", wknd_gross, fixed = T) |> as.numeric())

world_bxo_data <- left_join(intbxo, world) |>                                # join datasets
  filter(!is.na(wknd_gross))
world_bxo_data$continent = countrycode(sourcevar = world_bxo_data$region,    # retrieve continents
                                       origin = "country.name",
                                       destination = "continent")  
head(world_bxo_data, 3)

```
  
---

### Choropleth Country Plot w/ Labels

#### Example - Asia

- **Most** of the plot code that follows is review

  - There are a few new details:
    
    - `shadowtext` labels (see below)
    
    - modifying size of text elements (mentioned but not emphasized)

- **NOTES:** 

  - The R package `shadowtext` includes the command `geom_shadowtext`

  - `shadowtext` is useful for creating visible labels for all countries regardless of color

  - Deciding on units ($1000) and transformation (`log`) took some trial and error.
  
---
  
### Managing Data for Asia Chropleth Map

#### This R code creates the Asia Map dataset

```{r asia data for map}

asia_bxo_data <- world_bxo_data |>           # create asia box office dataset 
  filter(continent=="Asia") |>
  mutate(Gross = as.integer(wknd_gross), 
         wknd_gross = wknd_gross/1000) 

asia_nms <- asia_bxo_data |>                         # create dataset of country names 
  select(region, long, lat, group, continent) |>     # median lat and long used for position
  group_by(continent, region) |>
  summarize(nm_x=median(long, na.rm=T),
            nm_y=median(lat, na.rm=T)) |>
  filter(!is.na(nm_x) | !is.na(nm_y))

asia_bxo_data <- inner_join(asia_bxo_data, asia_nms) # merge datasets using an inner_join

```

---

### Asia Static Map with Log Transformation

```{r asia static map code}

(asia_bxo_map <- asia_bxo_data |>    # Creates the map that follows
   ggplot(aes(x=long, y=lat,
              group=group,
              fill=wknd_gross)) +
   geom_polygon() +
   theme_map() +
   coord_map("albers", lat0 = 39, lat1 = 45) +
   labs(fill= "Gross ($1K)",
        title="Weekend Gross ($ Thousands) in Asian Countries",
        subtitle="Weekend Ending 11/14/2022 - Data are Log-transformed",
        caption="Data Source: https://www.boxofficemojo.com") +
    
   scale_fill_continuous(type = "viridis",  trans="log",
                         breaks =c(1,10,100,1000,10000)) +
   geom_shadowtext(aes(x=nm_x, y=nm_y,label=region),
                   color="white",check_overlap = T,
                   show.legend = F, size=4) + 
                   
   theme(plot.title = element_text(size = 20),
         plot.subtitle = element_text(size = 15),
         plot.caption = element_text(size = 10),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 15),
         plot.background = element_rect(colour = "darkgrey", fill=NA, size=2)))

```


---

### Asia Interactive Map with Log Transformation

Map projection appears incorrect

```{r asia interactive map, warning=FALSE, message=FALSE}

asia_bxo_map_intr <- asia_bxo_data |>
   ggplot(aes(x=long, y=lat, group=group)) +
   geom_polygon(aes(fill=Gross)) +
   geom_line(aes(text=region, color=Gross), show.legend=F, alpha = 0.01) +  # used for interactive labels
   theme_map() +
   coord_map("albers", lat0 = 39, lat1 = 45) +
   labs(fill= "Gross", color="",
        title="Asian Countries - Weekend Gross - Weekend Ending 11/14/22"
        ) +
   scale_fill_continuous(type = "viridis",  trans="log",
                         breaks =c(1,10,100,1000,10000, 100000, 1000000),
                         labels=c("1", "10", "100", "1K", "10K", "100K", "1M")) +
   theme(plot.title = element_text(size = 15),
         legend.text = element_text(size = 10),
         legend.title = element_text(size = 10),
         legend.background = element_rect(colour = "lightgrey", fill=NA, size=0.5),
         panel.border = element_rect(colour = "lightgrey", fill=NA, size=2))

(asia_intr_map <- ggplotly(asia_bxo_map_intr, 
                           tooltip = c("text","color")))

```

---


### Lecture 19 In-class Exercise

- If you project includes data that can be mapped, this exercise will be helpful

- Details like text size, `shadowtext`, and data transformations can all greatly improve data clarity.

- You can choose to create a static map with shadow text or an interactive map

  - If you create static map, submit the .png file
  
  - If you create an interactive map, take screenshot with an interactive label showing

---

### Europe Box Office Map

- Copy and paste R code from previous chunks

- Convert it to create dataset for Europe map and one of the maps shown.

- This requires going through code line by line and making the following changes:

  - change `asia` to `euro`
  
  - change "Asia" to "Europe"
  
  - In static map, country labels in map may need to be slightly smaller (size=3)
  
---
  
    
### Europe Map Data

Creates data for Europe Map

```{r europe data for map}

euro_bxo_data <- world_bxo_data |>           # create europe box office dataset 
  filter(continent=="Europe" & region != "Russia") |>
  mutate(Gross = as.integer(wknd_gross), 
         wknd_gross = wknd_gross/1000) 

euro_nms <- euro_bxo_data |>                         # create dataset of country names 
  select(region, long, lat, group, continent) |>     # median lat and long used for position
  group_by(continent, region) |>
  summarize(nm_x=median(long, na.rm=T),
            nm_y=median(lat, na.rm=T)) |>
  filter(!is.na(nm_x) | !is.na(nm_y))

euro_bxo_data <- inner_join(euro_bxo_data, euro_nms) # merge datasets using an inner_join

```

---

### Europe Static Map with Log (LN) Transformation

Student will create this map or interactive one by adapting Asia Map code

```{r europe static map}

# copy, paste, and modify asia static map code in this chunk


```

---

### European Interactive Map with Log (LN) Transformation

Students will create this map or static one by adapting Asia Map code (projection is not correct).

```{r euro interactive map, warning=FALSE, message=FALSE}

# copy, paste, and modify asia interactive map code in this chunk

```


---

### Managing Projects 
  
- At this point, much of this should be review

- After break, I will spend a little time walking you through a consulting project

  - Project involved segmenting and rejoining data in multiple ways
  
  - Client asked for additional analyses months later

- Documentation is key

  - Take good notes and keep README file updated

- I use a Markdown files for everything, even work I don't present to client.
  
  - Ideal format for wiring notes between code
  
---

### What Goes where in a BUA 455 R Projects
  
#### **code_data_output folder** should have: 
  
  - All raw .csv files needed

  - ***NO data management should be done in Excel.***
  
  - Any .png or other graphics files needed
  
  - Dashboard .rmd file (R Markdown file)

  - Dashboard .html file (Dashboard presentation)
  
  - NOTE: As you progress in data management, code, data, and output may be in separate folders
    
    - requires specifying folder and file name
    
---

### What Goes where in a BUA 455 R Projects

#### **outer folder** should have

  - code_data_output folder (see above)

  - Complete and accurate README.txt file

  - .Rproj file that is functional 

- Other files can be stored in project **outer** file if needed

- If other files are stored in this outer folder they must be catalogued in the README file

---

### Thursday 11/17 -  New Material Begins Here

#### One more Set of Geographic Data Examples

- Student Questions Indicate there is interest in this material.

- Provides review of previous data management skills along with new data viz skills

- Today's examples can be applied to state data or to country data 

  - still unsure of world projections but can do more research
  
- Examples of Data that can be plotted by state

  - Average costs and expenditures by state of specific goods or services

  - Demographic data

  - Voting and tex information

  - Sports/Arts/Entertainment/Education investments and expenditures
  
- Today's examples will also show a map of data filtered by region

---

### US State Map Data
  
```{r combine state polygons with state population data from R}

us_states <- map_data("state") |>          # state polygons (from R)
  select(long:region) |>
  rename("state" = "region")

state_abbr <- state_stats |>               # many useful variables in this dataset
  select(state, abbr) |>
  mutate(state = tolower(state))

state_pop <- county_2019 |>               # data by county (aggregated by state)
  select(state, pop) |>
  mutate(state=tolower(state),
         popM = pop/1000000) |>
  group_by(state) |>
  summarize(st_popM = sum(popM, na.rm=T)) |>
  full_join(state_abbr)

statepop_map <- left_join(us_states, state_pop) # used left join to filter to lower 48 states
                                                # lat/long not available for Hi and AK

```

---

### Adding State Midpoint (centroid) Lat and Long
  
- On Tuesday, country labels were added to the static map using each polygon's (country)  median latitude and longitude 
  
- Medians don't work well for U.S. because many states are oddly shaped and small.

- Alternative: [use centroid for each state polygon](https://www.latlong.net/category/states-236-14.html)

  - Centroid is another term for midpoint

  - Saved data as .csv file named `state_coords.csv` (included)
   
     - Data did not include D.C. but those coordinates were found elsewhere

     - Added `state_coords` to `state_match` to verify agreement and added DC there.

     - New dataset created: `state_match_check`

- Final dataset for plot created: `state2019pop_map`

---

### Code for Addings State Midpoints (centroids) to data

```{r add lat and long of state midpoints (centroid)}

state_coords <- read_csv("state_coords.csv", show_col_types = F,
                         col_names = c("state", "m_lat", "m_long")) |>
  mutate(state = gsub(", USA", "", state, fixed=T),
         state = gsub(", the USA", "", state, fixed=T),
         state = gsub(", the US", "", state, fixed=T),
         state = tolower(state))

state <- "district of columbia"        # save values for dc
m_lat <- 38.9072
m_long <- -77.0369
dc <- tibble(state, m_lat, m_long)     # create dataset of dc data ( 1 obs)
state_coords <- bind_rows(state_coords, dc) # add dc to state_coords

rm(dc, state, m_lat, m_long)           # remove temporary values from global
statepop_map <- left_join(statepop_map, state_coords) # centroids to data

```

---

### State Population Plot
  
- Similar to plots from Tuesday with a few changes

  - Added borders to states by adding `color="darkgrey"` to `geom_polygon` command.

  - Used State abbreviations for state labels.

  -  Made State text labels smaller (Size = 2)

  - Changed breaks for log scaled population legend

- These details seem minor but they take time and trial and error.

---

### R Code for US State Pop. Map (without transformation)

```{r code for us states pop map no transformation}

st_pop <- statepop_map |>
    ggplot(aes(x=long, y=lat, group=group, fill=st_popM)) +
    geom_polygon(color="darkgrey") +
    theme_map() +
    coord_map("albers", lat0 = 39, lat1 = 45) +
    scale_fill_continuous(type = "viridis")+
    theme(legend.position = "bottom",
          legend.key.width = unit(1, "cm"),
          plot.background = element_rect(colour = "darkgrey", fill=NA, size=2)) +
    geom_shadowtext(aes(x=m_long, y=m_lat, label=abbr),
                    color="white", check_overlap = T,
                    show.legend = F, size=2) + 
    labs(fill= "Pop. in Millions", title="Population by State",
         subtitle="Unit is 1 Million People",
         caption= "Not Shown: HI: 1.42 Million   AK: 0.74 Million
         Data Source: https://CRAN.R-project.org/package=usdata")  
  
  

```

---

### US State Pop. Map (without transformation)

```{r us states pop map no transformation, fig.dim=c(15,7), fig.align='center'}

st_pop

```

---

### R Code for US State Pop. Map (with log transformation)

```{r code for us states pop map with log transformation}

st_lpop <- statepop_map |>
    ggplot(aes(x=long, y=lat, group=group, fill=st_popM)) +
    geom_polygon(color="darkgrey") +
    theme_map() +
    coord_map("albers", lat0 = 39, lat1 = 45) +
    scale_fill_continuous(type = "viridis", trans="log",
                          breaks=c(0,1,2,3,5,10,20,35)) +
    theme(legend.position = "bottom",
          legend.key.width = unit(1, "cm"),
          plot.background = element_rect(colour = "darkgrey", fill=NA, size=2)) +
    geom_shadowtext(aes(x=m_long, y=m_lat, label=abbr),
                    color="white", check_overlap = T,
                    show.legend = F, size=2) + 
    labs(fill= "Pop. in Millions", title="Population by State",
         subtitle="Unit is 1 Million People - Log Transformed",
         caption= "Not Shown: HI: 1.42 Million   AK: 0.74 Million
         Data Source: https://CRAN.R-project.org/package=usdata")

```

---

### US State Pop. Map (with log transformation)

```{r us states pop map log transformation, fig.dim=c(15,7), fig.align='center'}

st_lpop

```

---

### R Code for Interactive US State Pop. Map (with log transformation)

```{r code for us interactive map with log transformation}

statepop_map <- statepop_map  |>
    mutate(int_text = paste(abbr, "\n", round(st_popM,2))) 
st_lpop_int <- statepop_map  |>           
    ggplot(aes(x=long, y=lat, group=group, fill=st_popM)) +
    geom_polygon(aes(text=int_text), color="darkgrey") +
    #geom_line(aes(text=abbr, size=st_popM*1000000),
    #          show.legend=F, alpha = 0.01) +
    theme_map() +
    coord_map("albers", lat0 = 39, lat1 = 45) +
    scale_fill_continuous(type = "viridis", trans="log",
                          breaks=c(0,1,2,3,5,10,20,35)) +
    theme(legend.position = "bottom",
          legend.key.width = unit(1, "cm"),
          legend.background = element_rect(colour = "lightgrey", fill=NA, size=0.5),
          panel.border = element_rect(colour = "lightgrey", fill=NA, size=2)) +
    geom_shadowtext(aes(x=m_long, y=m_lat, label=abbr),
                    color="white", check_overlap = T,
                    show.legend = F, size=2) + 
    labs(fill= "Pop. in Millions", title="Population by State",
         subtitle="Unit is 1 Million People - Log Transformed",
         caption= "Not Shown: HI: 1.42 Million   AK: 0.74 Million
         Data Source: https://CRAN.R-project.org/package=usdata")

st_lpop_int <- ggplotly(st_lpop_int, 
                           tooltip = "text") # interactive component


```

---

### Interactive State Map (draft format)

ggplotly removes projection and other map elements

```{r us state interactive map, echo=F, fig.dim=c(10,7), fig.align='center'}

st_lpop_int

```

---

### To log or not to log

In this class, we visualize data using `ggplot` (and now `ggplotly`), `hchart`, `dygraph`

If you want to explore (not present), you can use base graphics

- Base graphics could also be used to make polished vizualizations but the code is much longer and more tedious than `ggplot`


```{r base graphics plots, fig.dim=c(4, 6), fig.align='center'}

par(mfrow=c(2,1)) # stacks base graph plots
hist(statepop_map$st_popM, main="")
hist(log(statepop_map$st_popM), main="")
par(mfrow=c(1,1)) # resets base graph options

```


---

### Filtering a Map to a Region

- Map techniques above can also be used for a region
- Demo that follows uses an education dataset with data filtered to 10 Northeastern states

```{r import modify filter education data}

edu <- read_csv("education by state.csv", skip=3, show_col_types = F, # import data
                col_names = c("state", "pop_over_25", "pop_hs", "pct_hs",
                              "pop_bachelor", "pct_bachelor", 
                              "pop_advanced","pct_advanced")) 
edu1 <- edu |>
  select(state, pop_bachelor, pct_bachelor) |>
  mutate(state = str_trim(state) |> tolower(),
         pop_bachelor1K = pop_bachelor/1000,
         pct_bachelor = gsub("%","", pct_bachelor, fixed = T) |> as.numeric()) |> 
  filter(state %in% c("maine", "massachusetts", "connecticut" , "rhode island",
                      "vermont", "new hampshire", "new york", "new jersey", "pennsylvania",
                      "delaware")) |> glimpse()

```

---

### Exploratory Bachelor Degree Data  Plots (Base-R) 

```{r base R scatterplot and histogram, fig.dim=c(12,7), fig.align='center'}

par(mfrow=c(1,2))
hist(edu1$pop_bachelor1K, main="")
plot(edu1$pop_bachelor1K, edu1$pct_bachelor, main="")
par(mfrow=c(1,1))

```

---

#### Week 12 In-class Exercises
  
***TurningPoint Session ID: bua455s22***

#### TP Question 1 (L20)
  
What exploratory plot command (base R code shown) is good for checking if the variable you want to plot is right skewed and might need to be log transformed?

<br>

#### TP Question 2 (L20)
  
Based on the histogram for the northeastern area of the U.S, which includes only 10 states, do these data appear skewed?

---

### Add Education Data to Map Data

In the chunk below we start from scratch with state data.
This chunk does not depend on the data being imported and managed in a previous chunk.

```{r join edu data with state map and state abbr data}

us_states <- map_data("state") |>    # state polygons (from R)
  select(long:region) |> rename("state" = "region")
state_abbr <- state_stats |>         # state abbreviations 
  select(state, abbr) |> mutate(state = tolower(state))

edu1 <- left_join(edu1, state_abbr)      # left join to maintain filter to NE states
edu_NE_map <- left_join(edu1, us_states) # left join to maintain filter to NE states
state_coords <- read_csv("state_coords.csv", show_col_types = F,       # add in state midpoints (centroids)
                         col_names = c("state", "m_lat", "m_long")) |>
  mutate(state = gsub(", USA", "", state, fixed=T),
         state = gsub(", the USA", "", state, fixed=T),
         state = gsub(", the US", "", state, fixed=T),
         state = tolower(state))
edu_NE_map <- left_join(edu_NE_map, state_coords)  # left join to maintain filter to NE states

```


---

### Code for Regional Map 1 - Population with Bachelor's Degree
  
[Data Source - Wikipedia](https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_educational_attainment)

```{r NE edu map pop}

ne_edu_pop <- edu_NE_map |>         
  ggplot(aes(x=long, y=lat, group=group, fill=pop_bachelor1K)) +   # pop in 1000s
  geom_polygon(color="darkgrey") +
  theme_map() +
  coord_map("albers", lat0 = 39, lat1 = 45) +
  scale_fill_continuous(type = "viridis", trans="log",             # log transformation
                        breaks = c(100, 500, 1000, 5000))+
  theme(legend.position = "bottom",
        legend.key.width = unit(1, "cm")) +
  geom_shadowtext(aes(x=m_long, y=m_lat, label=abbr),
                  color="white", check_overlap = T, show.legend = F, size=3) + 
  labs(fill= "Unit: 1000 People", 
       title="NE States: Pop. with a Bachelor's Degree",)
```

---

### Code for Regional Map 2 - Percentage of People with Bachelor's Degree
  
[Data Source - Wikipedia](https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_educational_attainment)

```{r NE edu map pct}

ne_edu_pct <- edu_NE_map |>
  ggplot(aes(x=long, y=lat, group=group, fill=pct_bachelor)) +        # percent data
  geom_polygon(color="darkgrey") +
  theme_map() +
  coord_map("albers", lat0 = 39, lat1 = 45) +
  scale_fill_continuous(type = "viridis",                             # no transformation needed
                        breaks = c(32, 34, 36, 38, 40, 42, 44)) +
  theme(legend.position = "bottom",
        legend.key.width = unit(1, "cm")) +
  geom_shadowtext(aes(x=m_long, y=m_lat, label=abbr),
                  color="white", check_overlap = T, show.legend = F, size=3) + 
  labs(fill= "Unit: %", title="NE States: Percent with a Bachelor's Degree")

```

---

### Population and Percentage with Bachelors Degree Side by Side

```{r display of NE pop and pct maps, fig.dim=c(15,7), fig.align='center'}

grid.arrange(ne_edu_pop, ne_edu_pct, ncol=2)
grid.rect(width = .98, height = .98, gp = gpar(lwd = 2, col = "darkgrey", fill = NA))

```

---

### Rpubs Exercise

#### **RPubs** (Review from Tuesday)

- If you want to publish your dashboard or any HTML file you create in R, you can do so for free.  

- R has a public online repository called [RPubs](https://rpubs.com/).  

- I am not requiring students to use it for their projects, but it is useful if you want post something online and provide the link to it.

- This is particularly useful if your dashboard is large and slow to knit

  - Being able to post the link instead of the .html file saves time

- As an in class exercise on Thursday, I will ask you each to create an account and publish your HW 5 - Part 1 dashboard html file 

  - This will be useful to experiment with
  
    - You can see how publishing changes the appearance of your panels and text.
  
    - In previous semesters, some students have saved their final dashboard online and linked it to their resumes and LinkedIn profiles.
    
---

### Lecture 20 In-class Exercise 
  
**`1.`** Open your HW 5 - Part 1.Rmd file and knit it to create your dashboard. 

- Make sure this file has your name in the header.

- It is okay if you haven't revised it yet for HW 5 - Part 2 
   
  - Rminder HW 5 - Part 2 is due tomorrow.
  
  - If you don't have HW 5 - Part 1 done, you can use your html file from another HW Assignment, e.g. HW 4.
   
**`2.`** Click the Rpubs icon, create a free account, and publish your html file.

- If RStudio asks to install additional packages to complete the publishing process, click `Yes`.

**`3.`** Submit the link to your published file on Blackboard.

**`4.`** A Link to your published file must be submitted by Friday 11/17/22 at midnight to count for class participation today.

---

### Next Week:

#### Additional Topics

- Ask me questions about your project (Others may benefit)

- I have topics including

  - Managing a consulting project from begining to end
  
  - formatting complex tables using the `gt` package

- Time permitting, I will also demo 

  - knitting R Markdown to different formats: word, powerpoint, etc.
  
  - Next Gen. RStudio publishing using Quarto 
  
    - files are .qmd instead of .Rmd and rendering appears to be streamlined
  
---

### Next Week:

#### Review of Skillset Terminology

Now that you are (almost) done with BUA 455 and more so, when you graduate you have a very useful set of skills

- We talked about these skills in October because I had a couple questions from students preparing for internship interviews.

- Explaining these skills to others is a challenge

- I will spend a little time talking about how to explain those skills to other people

- Preview: It took me decades to figure out how to talk about what I do.

  - Increased interest in Data Science and Analytics has resulted in better terminology
  
  - [White Paper from DataCamp provides an excellent blueprint](https://drive.google.com/file/d/1_VoM3D6tPftjZpXCnTL8SKYBlOM_4KjG/view?usp=sharing)
  
---


### **Key Points from Week 12**
  
- **HW 2 - Part 2**

  - Due Friday, 11/18/22
    
- **More with Geographic Data**

   - Adding Shadow Text
   - Introduction to Interactive Maps
   - Projection Needs more tinkering

- **Project Management**

   - skills emphasized throughout course
   - managing course project this way is beneficial
   
- **Publishing Work on RPubs**

   - Useful for publishing and linking to work
    

**You may submit an 'Engagement Question or Comment' about Week 12 lectures until Thursday, 11/17, at midnight on Blackboard.**
